Evaluating Class Imbalance

### 2019-07-09 Scripts/comparing_tad_regions_across_cl_using_vd.Rmd
added 5kb results

@@

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=20)))
grid.newpage()

>>>>

### 5kb

```{r}
#bounds_f_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/bounds_f.rds")
#bounds_f_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/bounds_f.rds")

#res <- makeVennDiagram(Peaks=list(bounds_f_gm12878_5kb, bounds_f_K562_5kb),
#                       NameOfPeaks=c("GM12878", "K562"))

#venn_5kb <- venn_cnt2venn(res$vennCounts)
#plot(venn_5kb)

binslist_gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5.rds")
binslist_gm12878_5kb_center <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/training_testing/binslist5_center.rds")
mcols(binslist_gm12878_5kb)$y <- mcols(binslist_gm12878_5kb_center)$y
binslist_gm12878_5kb <- binslist_gm12878_5kb[mcols(binslist_gm12878_5kb)$y==1]

binslist_K562_5kb <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5.rds")
binslist_K562_5kb_center <- readRDS("Z:/TAD_data_analysis/K562/5kb/training_testing/binslist5_center.rds")
mcols(binslist_K562_5kb)$y <- mcols(binslist_K562_5kb_center)$y
binslist_K562_5kb <- binslist_K562_5kb[mcols(binslist_K562_5kb)$y==1]

res <- makeVennDiagram(Peaks=list(binslist_gm12878_5kb, binslist_K562_5kb),
                       NameOfPeaks=c("GM12878", "K562"))

venn_5kb <- venn_cnt2venn(res$vennCounts)
venn_5kb <- compute.Venn(venn_5kb)
gp <- VennThemes(venn_5kb)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
#plot(venn_5kb)

@@

gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_5kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("5 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_10kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("10 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_25kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("25 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_50kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("50 kb", gp=gpar(fontsize=20)))
grid.newpage()
gridExtra::grid.arrange(grid::grid.grabExpr(plot(venn_100kb, gp = gp, show=list(Universe=FALSE))), top=textGrob("100 kb", gp=gpar(fontsize=20)))
grid.newpage()

### 2019-07-09 Scripts/evaluating_imbalance_ratios.Rmd
added 5kb results

```{r}
cl.per.chr <- character()
res.per.chr <- character()
chr.per.chr <- character()
bins.per.chr <- numeric()
bounds.per.chr <- numeric()
ir.per.chr <- numeric()
tads.per.chr <- numeric()

chrs <- paste0("chr", c(1:8,10:22))
for(i in c("GM12878","K562")){
  for(j in c("10kb", "25kb","50kb","100kb")){
    for(k in 1:length(chrs)){
      binslist_dat_center <- readRDS(paste0("Z:/TAD_data_analysis/",
                                            i,
                                            "/",
                                            j,
                                            "/training_testing/binslist",
                                            gsub("kb","",j),
                                            "_center.rds"))

@@

irtab <- cbind.data.frame(cl.per.chr,
                          res.per.chr,
                          chr.per.chr,
                          bins.per.chr,
                          tads.per.chr,
                          bounds.per.chr,
                          ir.per.chr)
colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir")
irtab$res <- factor(irtab$res, levels=c("10kb","25kb","50kb","100kb"))

irtab_summ <- irtab %>%
  group_by(cl, res) %>%
  dplyr::summarise(AveBins = mean(bins, na.rm = TRUE),
            AveBinsSD = sd(bins, na.rm = TRUE),
            AveTADs = mean(tads, na.rm = TRUE),
            AveTADsSD = sd(tads, na.rm = TRUE),
            AveBounds = mean(bounds, na.rm = TRUE),
            AveBoundsSD = sd(bounds, na.rm = TRUE),
            AveIR = mean(ir, na.rm = TRUE),
            AveIRSD = sd(ir, na.rm = TRUE))

irtab_summ_med <- irtab %>%
  group_by(cl, res) %>%
  dplyr::summarise(MedBins = median(bins, na.rm = TRUE),
            MedBinsIQR = IQR(bins, na.rm = TRUE),
            MedTADs = median(tads, na.rm = TRUE),
            MedTADsIQR = IQR(tads, na.rm = TRUE),
            MedBounds = median(bounds, na.rm = TRUE),
            MedBoundsIQR = IQR(bounds, na.rm = TRUE),
            MedIR = median(ir, na.rm = TRUE),
            MedIRIQR = IQR(ir, na.rm = TRUE))

@@

```{r}
a <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,27000) +
  scale_fill_discrete(name="Cell Line") +
  ggtitle("10 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=10),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

b <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,27000) +
  scale_fill_discrete(name="Cell Line") +
  ggtitle("25 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=10),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

c <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,27000) +
  scale_fill_discrete(name="Cell Line") +
  ggtitle("50 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=10),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

d <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,27000) +
  scale_fill_discrete(name="Cell Line") +
  ggtitle("100 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=10),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(a,b,c,d,
                    ncol=4,
                    nrow=1)
figure
annotate_figure(figure,
    #bottom = text_grob("Cell Line", color = "black", size = 20),
    left = text_grob("Number of TAD Boundary Regions", color = "black", rot = 90, size=20)
)

@@

>>>>

```{r}
cl.per.chr <- character()
res.per.chr <- character()
chr.per.chr <- character()
bins.per.chr <- numeric()
bounds.per.chr <- numeric()
ir.per.chr <- numeric()
tads.per.chr <- numeric()
pi.per.chr <- numeric()

chrs <- paste0("chr", c(1:8,10:22))
for(i in c("GM12878","K562")){
  for(j in c("5kb", "10kb", "25kb","50kb","100kb")){
    for(k in 1:length(chrs)){
      binslist_dat_center <- readRDS(paste0("Z:/TAD_data_analysis/",
                                            i,
                                            "/",
                                            j,
                                            "/training_testing/binslist",
                                            gsub("kb","",j),
                                            "_center.rds"))

@@

irtab <- cbind.data.frame(cl.per.chr,
                          res.per.chr,
                          chr.per.chr,
                          bins.per.chr,
                          tads.per.chr,
                          bounds.per.chr,
                          ir.per.chr,
                          pi.per.chr)
colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir","pi")
irtab$res <- factor(irtab$res, levels=c("5kb","10kb","25kb","50kb","100kb"))

irtab_summ <- irtab %>%
  group_by(cl, res) %>%
  dplyr::summarise(AveBins = mean(bins, na.rm = TRUE),
            AveBinsSD = sd(bins, na.rm = TRUE),
            AveTADs = mean(tads, na.rm = TRUE),
            AveTADsSD = sd(tads, na.rm = TRUE),
            AveBounds = mean(bounds, na.rm = TRUE),
            AveBoundsSD = sd(bounds, na.rm = TRUE),
            AveIR = mean(ir, na.rm = TRUE),
            AveIRSD = sd(ir, na.rm = TRUE),
            AvePI = mean(pi, na.rm = TRUE),
            AvePISD = sd(pi, na.rm = TRUE))

irtab_summ_med <- irtab %>%
  group_by(cl, res) %>%
  dplyr::summarise(MedBins = median(bins, na.rm = TRUE),
            MedBinsIQR = IQR(bins, na.rm = TRUE),
            MedTADs = median(tads, na.rm = TRUE),
            MedTADsIQR = IQR(tads, na.rm = TRUE),
            MedBounds = median(bounds, na.rm = TRUE),
            MedBoundsIQR = IQR(bounds, na.rm = TRUE),
            MedIR = median(ir, na.rm = TRUE),
            MedIRIQR = IQR(ir, na.rm = TRUE),
            MedPI = median(pi, na.rm = TRUE),
            MedPIIQR = IQR(pi, na.rm = TRUE))

@@

```{r}
a <- ggplot(bounds_df[which(bounds_df$res=="5kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("5 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

b <- ggplot(bounds_df[which(bounds_df$res=="10kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("10 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

c <- ggplot(bounds_df[which(bounds_df$res=="25kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("25 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

d <- ggplot(bounds_df[which(bounds_df$res=="50kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("50 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

e <- ggplot(bounds_df[which(bounds_df$res=="100kb"),], aes(x=cl, y=TotBounds, fill=cl))+
  geom_bar(stat="identity", position="dodge")+
  theme_minimal() +
  theme_bw()+
  xlab("") + ylab("") + ylim(0,30000) +
  scale_fill_discrete(name="Cell Line") +
  scale_y_continuous(limits = c(0,30000),
                     breaks=c(0,10000,20000,30000),
                     labels=c("0"="0", "10000"="10", "20000"="20", "30000"="30")) +
  ggtitle("100 kb") +
  guides(fill=FALSE) +
  theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(a,b,c,d,e,
                    ncol=5,
                    nrow=1)
figure
annotate_figure(figure,
    #bottom = text_grob("Cell Line", color = "black", size = 20),
    left = text_grob("Number of TAD Boundary\nRegions (thousands)", color = "black", rot = 90, size=20)
)

@@

## PI Plots

```{r}
a <- ggplot(irtab[which(irtab$res=="5kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
 stat_boxplot(geom ='errorbar', width = 0.2) + 
 geom_boxplot() +
 theme_minimal() +
 theme_bw()+
 xlab("") + ylab("") + ylim(0,.2) +
 ggtitle("5 kb") +
 guides(fill=FALSE) +
 guides(color=FALSE) +
 theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

b <- ggplot(irtab[which(irtab$res=="10kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
 stat_boxplot(geom ='errorbar', width = 0.2) + 
 geom_boxplot() +
 theme_minimal() +
 theme_bw()+
 xlab("") + ylab("") + ylim(0,.2) +
 ggtitle("10 kb") +
 guides(fill=FALSE) +
 guides(color=FALSE) +
 theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

c <- ggplot(irtab[which(irtab$res=="25kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
 stat_boxplot(geom ='errorbar', width = 0.2) + 
 geom_boxplot() +
 theme_minimal() +
 theme_bw()+
 xlab("") + ylab("") + ylim(0,.2) +
 ggtitle("25 kb") +
 guides(fill=FALSE) +
 guides(color=FALSE) +
 theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

d <- ggplot(irtab[which(irtab$res=="50kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
 stat_boxplot(geom ='errorbar', width = 0.2) + 
 geom_boxplot() +
 theme_minimal() +
 theme_bw()+
 xlab("") + ylab("") + ylim(0,.2) +
 ggtitle("50 kb") +
 guides(fill=FALSE) +
 guides(color=FALSE) +
 theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

e <- ggplot(irtab[which(irtab$res=="100kb"),], aes(x=cl, y = pi, fill=cl, color=cl))  + 
 stat_boxplot(geom ='errorbar', width = 0.2) + 
 geom_boxplot() +
 theme_minimal() +
 theme_bw()+
 xlab("") + ylab("") + ylim(0,.2) +
 ggtitle("100 kb") +
 guides(fill=FALSE) +
 guides(color=FALSE) +
 theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(a,b,c,d,e,
                    ncol=5,
                    nrow=1)
figure
annotate_figure(figure,
    #bottom = text_grob("Cell Line", color = "black", size = 20),
    left = text_grob("Proportion of Imbalance", color = "black", rot = 90, size=20)
)
